---
title: "TMDL_Rankings"
author: "Alene Onion"
date: "2/8/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#  {.tabset}

## Impaired Waters

impaired waterbodies that are not NYC reservoirs

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE}
#merging lake id with the DOH ID

rm(list=ls())
#read in data
#Script to read in new database
library(tidyverse)
# library(ggmap)
# library(ggrepel)
# library(rgdal)
# library(sp)
# library(spatialEco)
# library(tidyverse)
library(knitr)
#Reading in new database
setwd("C:/Users/leneo/Dropbox/Alene/Rscripts/Current")
location<-read.csv("new_database/L_LOCATION.csv",na.strings=c("","NA"), stringsAsFactors=FALSE)
lake<-read.csv("new_database/L_LAKE.csv",na.strings=c("","NA"), stringsAsFactors=FALSE)
results<-read.csv("new_database/results.csv",na.strings=c("","NA"), stringsAsFactors=FALSE)
setwd("C:/Users/leneo/Dropbox/Alene/Rscripts/Modeling_Workgroup")

#pull lake id and names for each PWL
lake1<-lake %>% select(LAKE_HISTORY_ID,LAKE_WATERBODY_NAME) %>% distinct()
location1<-location %>% select(LAKE_HISTORY_ID,LOCATION_HISTORY_ID,LOCATION_PWL_ID) %>% distinct()
locs<-merge(lake1,location1,by=c('LAKE_HISTORY_ID'),all.x=TRUE)

draft<-read.csv("C:/Users/leneo/Dropbox/Alene/Rscripts/Modeling_Workgroup/2022_stayCALM_ponded_internal-draft-assessments.csv")
draft<-draft %>% 
  select(seg_id:parameter) %>% 
  distinct() %>% 
  rename(LOCATION_PWL_ID=seg_id) %>% 
  mutate(value=1)

#add names
draft<-merge(draft,locs,by=c('LOCATION_PWL_ID'),all.x=TRUE)
#restrict to those that have confirmed assessments
draft<-draft %>% 
  filter(grepl("IR5_impaired_confirmed",use_assessment)) %>% 
  distinct()

#Remove NYC reservoirs
draft<-draft %>% filter(!(LAKE_HISTORY_ID %in% c('1302WES0067','1302BOY0076','1302EAS0089','1302BOG0086','1302MID0062','1302DIV0083','1302CRO0059',
                                                 '1302TIT0103','1302CRO0109','1302AMA0050','1302MUS0044A','1302NEW0044',
                                                 '1702KEN1063','1302GIL0061','1302GLE0074','1302KIR0052','1404CAN0402A','1403PEP0358A',
                                                 '1306RON0815A','1402NEV0058B','1307ASH0848','1202SCH0638A','1301JER1042')))


#tally results
junk<-draft %>% 
  select(LOCATION_PWL_ID,use,use_assessment) %>% distinct() %>% 
  group_by(use_assessment,use) %>% 
  summarize(n=n()) %>% 
  ungroup() %>% 
  spread(use_assessment,n,fill=NA)
library(kableExtra)
kable(junk)
rm(list=setdiff(ls(), c("newdata",'draft','location','results')))
```

## Map

The following map plots the impaired ponded waters under each designated use category.

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE}
sites<-draft %>% select(LOCATION_PWL_ID,waterbody,use) %>% distinct()

coordinates<-location %>% 
  filter(!is.na(LOCATION_X_COORDINATE),!is.na(LOCATION_Y_COORDINATE)) %>% 
  arrange(LOCATION_PWL_ID,LOCATION_TYPE) %>% 
  distinct(LOCATION_PWL_ID,.keep_all = TRUE) %>% 
  select(LOCATION_PWL_ID,LOCATION_X_COORDINATE,LOCATION_Y_COORDINATE) %>% 
  distinct()
sites<-merge(sites,coordinates,by=c('LOCATION_PWL_ID'),all.x = TRUE)

library(ggmap)
library(ggrepel)
sites1<-sites %>% filter(!is.na(LOCATION_X_COORDINATE),!is.na(LOCATION_Y_COORDINATE))

nybox<-make_bbox(sites1,lon=LOCATION_X_COORDINATE,lat=LOCATION_Y_COORDINATE)

print(ny.map1<-qmap(nybox,source="osm",maptype="terrain",color="bw")+
  geom_point(data=sites1,aes(x=LOCATION_X_COORDINATE,y=LOCATION_Y_COORDINATE,label=LOCATION_PWL_ID,colour=use),size=1)+
    facet_wrap(~use))
```

Please note that several impaired waterbodies are not currently in our database:

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE}
sites1<-sites %>% filter(is.na(LOCATION_X_COORDINATE)|is.na(LOCATION_Y_COORDINATE)) %>% 
  select(LOCATION_PWL_ID,waterbody,use) %>% distinct()

kable(sites1)
rm(list=setdiff(ls(), c("newdata",'draft','location','results')))
```


## Parameters

The following table lists impairment parameters and the frequency they impaired each use.

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE}
params<-read.csv("C:/Users/leneo/Dropbox/Alene/Rscripts/Modeling_Workgroup/params.csv")
params<-params$parameter
nparams<-length(params)
draft1<-draft %>% select(LOCATION_PWL_ID,LAKE_HISTORY_ID,waterbody,use,use_assessment,parameter) %>% distinct()
for(i in 1:nparams){
  draft1<-draft1 %>% 
    mutate(!!as.name(params[i]):=ifelse(grepl(params[i],parameter),1,0))
}
draft1<-draft1 %>% 
  gather(parameter,presence,-LOCATION_PWL_ID,-waterbody,-LAKE_HISTORY_ID,-use,-use_assessment,-parameter) %>% distinct() %>% 
  group_by(use,parameter) %>% 
  summarize(presence=sum(presence)) %>% 
  ungroup() %>% 
  filter(!is.na(presence)) %>% 
  spread(use,presence)

DT::datatable(draft1, extensions = 'Buttons', options = list(dom = 'Bfrtip',buttons = c('copy', 'csv', 'excel', 'pdf', 'print')))

rm(list=setdiff(ls(), c("newdata",'draft','location','draft1','results')))
```
## Lake Characteristics

The following table details the acreage, watershed acreage, depth (from the depth profile), and % land use categories for each impaired waterbody

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE}
#google search NLCD legend to learn what land use each VALUE_ field represents. They are given in % of total and the total acreage is given in the AreaSqKm field
land<-read.csv("C:/Users/leneo/Dropbox/Alene/Rscripts/Modeling_Workgroup/Statewide_Lake_Watershed_NLCD_2016_percentages_NHD_LakeID.csv")
land<-land %>% 
  select(Lake_ID,LkAcres,AreaSqKm,Elevation,VALUE_11,VALUE_21,VALUE_22,VALUE_23,VALUE_24,VALUE_31,
         VALUE_41,VALUE_42,VALUE_43,VALUE_52,VALUE_71,VALUE_81,VALUE_82,VALUE_90,VALUE_95) %>% distinct() %>% 
  rename(LAKE_HISTORY_ID=Lake_ID,
         Lake_Acres=LkAcres,
         Watershed_Area=AreaSqKm,
    Open_Water=VALUE_11,
         Developed_Open_Space=VALUE_21,
         Developed_Low_Intensity=VALUE_22,
         Developed_Medium_Intensity=VALUE_23,
         Developed_High_Intensity=VALUE_24,
         Barren_Land=VALUE_31, 
         Deciduous_Forest=VALUE_41,
         Evergreen_Forest=VALUE_42,
         Mixed_Forest=VALUE_43,
         Shrub_Scrub=VALUE_52, 
         Grasslands_Herbaceous=VALUE_71, 
         Pasture_Hay=VALUE_81, 
         Cultivated_Crops=VALUE_82, 
         Woody_Wetlands=VALUE_90, 
         Emergent_Herbaceous_Wetlands=VALUE_95)

draft3<-draft %>% 
  select(LAKE_HISTORY_ID,LOCATION_PWL_ID,waterbody,use,parameter) %>% 
  distinct() %>% 
  spread(use,parameter,fill=NA)

depth<-results %>% select(RSLT_LOCATION_HISTORY_ID,RSLT_PROFILE_DEPTH) %>% distinct() %>% 
  arrange(RSLT_LOCATION_HISTORY_ID,-RSLT_PROFILE_DEPTH) %>%
  distinct(RSLT_LOCATION_HISTORY_ID,.keep_all = TRUE) %>% 
  filter(!is.na(RSLT_PROFILE_DEPTH)) %>% 
  rename(LOCATION_HISTORY_ID=RSLT_LOCATION_HISTORY_ID)
lakes<-location %>% select(LAKE_HISTORY_ID,LOCATION_HISTORY_ID) %>% distinct()
depth<-merge(depth,lakes,by=c('LOCATION_HISTORY_ID'),all.x=TRUE)
depth<-depth %>% select(LAKE_HISTORY_ID,RSLT_PROFILE_DEPTH) %>% distinct()

draft3<-merge(draft3,depth,by=c('LAKE_HISTORY_ID'),all.x=TRUE)
draft3<-merge(draft3,land,by=c('LAKE_HISTORY_ID'),all.x=TRUE)


rm(list=setdiff(ls(), c("newdata",'draft','location','draft1','results','draft3')))
```

Lakes impaired for water_supply_use

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE}
water_supply<-draft3 %>% 
  filter(!is.na(source_of_water_supply)) %>% 
  rename(parameters=source_of_water_supply) %>% 
  select(-fishing,-primary_contact_recreation,-secondary_contact_recreation) %>% 
  distinct()
DT::datatable(water_supply, extensions = 'Buttons', options = list(dom = 'Bfrtip',buttons = c('copy', 'csv', 'excel', 'pdf', 'print')))
```


Lakes impaired for primary_contact_recreation

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE}
Primary<-draft3 %>% 
  filter(!is.na(primary_contact_recreation)) %>% 
  rename(parameters=primary_contact_recreation) %>% 
  select(-fishing,-source_of_water_supply,-secondary_contact_recreation) %>% 
  distinct()
DT::datatable(Primary, extensions = 'Buttons', options = list(dom = 'Bfrtip',buttons = c('copy', 'csv', 'excel', 'pdf', 'print')))
```


Lakes impaired for secondary_contact_recreation

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE}
Secondary<-draft3 %>% 
  filter(!is.na(secondary_contact_recreation)) %>% 
  rename(parameters=secondary_contact_recreation) %>% 
  select(-fishing,-source_of_water_supply,-primary_contact_recreation) %>% 
  distinct()
DT::datatable(Secondary, extensions = 'Buttons', options = list(dom = 'Bfrtip',buttons = c('copy', 'csv', 'excel', 'pdf', 'print')))
```

Lakes impaired for fishing

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE}
fishing<-draft3 %>% 
  filter(!is.na(fishing)) %>% 
  rename(parameters=fishing) %>% 
  select(-secondary_contact_recreation,-source_of_water_supply,-primary_contact_recreation) %>% 
  distinct()
DT::datatable(fishing, extensions = 'Buttons', options = list(dom = 'Bfrtip',buttons = c('copy', 'csv', 'excel', 'pdf', 'print')))
```

## Phosphorus

The distribution of size classes in lakes with phosphorus impairments in any designated use.
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE}
phosphorus<-draft3 %>% 
  filter(grepl("phosphorus",fishing)|
           grepl("phosphorus",secondary_contact_recreation)|
           grepl("phosphorus",primary_contact_recreation)|
           grepl("phosphorus",source_of_water_supply),
         !is.na(Lake_Acres)) %>% 
  distinct() %>% 
  mutate(size_class=ifelse(Lake_Acres<10,"<10",""),
         size_class=ifelse(Lake_Acres>10&Lake_Acres<25,"10-25",size_class),
         size_class=ifelse(Lake_Acres>25&Lake_Acres<50,"25-50",size_class),
         size_class=ifelse(Lake_Acres>50&Lake_Acres<125,"50-125",size_class),
         size_class=ifelse(Lake_Acres>125,">125",size_class),
         size_class=factor(size_class,levels=c('<10','10-25','25-50','50-125','>125'))) 
phos_size<-phosphorus %>% 
  group_by(size_class) %>% 
  summarize(n=n()) %>% 
  ungroup()
DT::datatable(phos_size, extensions = 'Buttons', options = list(dom = 'Bfrtip',buttons = c('copy', 'csv', 'excel', 'pdf', 'print')))
```

All the sites with phosphorus impairment of any designated use
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE}
DT::datatable(phosphorus, extensions = 'Buttons', options = list(dom = 'Bfrtip',buttons = c('copy', 'csv', 'excel', 'pdf', 'print')))
```